---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%"
)
```

# inconMore - More data for Computational Models of Simultaneous Consonance

`inconMore` is an R library that supplements simultaneous consonance
perception datasets originally provided by Peter Harrison’s wonderful `incon` library available at [https://github.com/pmcharrison/incon](https://github.com/pmcharrison/incon). incon contains a range of roughness and harmonicity models and some perceptual datasets. Here we offer extra datasets.

## Installation

You can install the current version of `inconMore` from Github by
entering the following commands into R:

```{r,echo=TRUE,eval=FALSE}
if (!require(devtools)) install.packages("devtools")
devtools::install_github("tuomaseerola/inconMore")
```

## Datasets

Currently the following datasets are implemented:

| dataset | Stimulus N| Study               |
| :------ | :----- |:-----------------------|
| art18   | 12     | Arthurs et al., 2018   |
| pop19   | 80     | Popescu et al., 2019   |
| lah20a   | 25    | Lahdelma & Eerola 2020  (Exp. 1) |
| lah20b   | 72    | Lahdelma & Eerola 2020  (Exp. 2)|
| bowl18   | 298   | Bowling et al., 2018     |
| jl12a    | 55    | Johnson-Laird et al., 2012 (Exp. 1)|
| jl12b    | 48    | Johnson-Laird et al., 2012 (Exp. 2)|
| sch03    | 12    | Schwartz et al., 2003|
| lah16    | 15    | Lahdelma & Eerola, 2016|


## Usage

The primary function is `inconMore`, which contains several datasets.

```{r, message=FALSE, warning=FALSE,results='asis'}
library(inconMore)
data <- inconMore::art18 # Arthurs and Timmers 2018
knitr::kable(head(data))
```

See the package’s inbuilt documentation, `?inconMore`, for further
details.

## Example 

``` {r,message=FALSE,warning=FALSE}
library(inconMore)
library(hrep)
library(incon)

chord <- hrep::pi_chord(inconMore::art18$pi_chord[[1]]) # major
incon(chord,model = 'hutch_78_roughness')
chord <- hrep::pi_chord(inconMore::art18$pi_chord[[3]]) # diminished
incon(chord,model = 'hutch_78_roughness')

```
## Citation

Eerola, T. & Lahdelma, I. (2021). More data for Computational Models of Simultaneous Consonance.


## References

Arthurs, Y., Beeston, A. V., & Timmers, R. (2018). Perception of isolated chords: Examining frequency of occurrence, instrumental timbre, acoustic descriptors and musical training. _Psychology of Music, 46(5)_, 662--681.

Bowling, D. L., Purves, D., & Gill, K. Z. (2018). Vocal similarity predicts the relative attraction of musical chords. _Proceedings of the National Academy of Sciences, 115(1)_, 216–221. https://doi.org/10.1073/pnas.1713206115

Johnson-Laird, P. N., Kang, O. E., & Leong, Y. C. (2012). On musical dissonance. _Music Perception: An Interdisciplinary Journal, 30(1)_, 19-35. https://doi.org/10.1525/mp.2012.30.1.19

Lahdelma, I. & Eerola, T. (2016). Mild dissonance preferred over consonance in single chord perception. _i-Perception, 7(3)_, 1-21. https://doi.org/10.1177/2041669516655812

Lahdelma, I. & Eerola, T. (2020). Cultural familiarity and musical expertise impact the pleasantness of consonance/dissonance but not its perceived tension. _Scientific Reports(10), 8693_. https://doi.org/10.1038/s41598-020-65615-8

Popescu, T., Neuser, M. P., Neuwirth, M., Bravo, F., Mende, W., Boneh, O., Moss, F. C., & Rohrmeier, M. (2019). The pleasantness of sensory dissonance is mediated by musical style and expertise. _Scientific Reports, 9(1070)_. https://doi.org/10.1038/s41598-018-35873-8

Schwartz, D. A., Howe, C. Q., & Purves, D. (2003). The statistical structure of human speech sounds predicts musical universals. Journal of Neuroscience, 23(18), 7160--7168. https://doi.org/10.1523/JNEUROSCI.23-18-07160.2003



